Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-07 Moltres.tex
bib is broken because its not clear which zotero directory was used to create the original.

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{noauthor_gif_2015}, this reactor concept has gained renewed research
interest in the past decade, with many new nuclear companies proposing both
fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,noauthor_-able_2017,scarlat_design_2014,noauthor_neutronics_2016}. Two
key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
utilization and no radiation damage constraint on attainable fuel
burn-up. Together, these attributes result in significantly reduced core fissile
inventories and spent nuclear fuel mass \cite{noauthor_gen_2008}.  
Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
burning actinides and extending fuel resources.

\gls{MSR} modeling efforts describe steady-state and
transient behavior. Krepel et. al. extended the in-house \gls{LWR}
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. That work compared DYN3D-MSR against
experimental \gls{MSRE} data and then used it to simulate local fuel channel
blockages as well as local temperature perturbations. In a similar vein, Kophazi
et. al. used iterative coupling between in-house three-dimensional neutronic and
one-dimensional heat conduction models DALTON and THERM to analyze normal 
\gls{MSRE} operation as well as channel-blocking-incident
transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
effects of heat transfer coefficients as well as thermal
coupling between fuel channels through moderator heat conduction. More recently,
Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
\gls{MSBR} using the commercial finite element package COMSOL
Multiphysics \cite{cammi_multi-physics_2011}. That work directly solved the 
fuel salt velocity field, used heterogeneous group constants
in fuel and moderator regions, and employed a software package (COMSOL)
intrinsically designed for coupled multi-physics simulation.

@@

Moltres is an open source code licensed under \gls{LGPL} terms so the 
\gls{MSR} community can freely use, interrogate, and improve it.  Its openness 
is a defining characteristic and promotes
quality through transparency and ease of peer review. In the era of
GitHub\cite{noauthor_build_nodate} and international scientific collaboration,
open and modern software practices must be employed in order for nuclear
engineering simulation capability to enable discovery and support the regulatory
needs presented by new reactor designs. In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to
enable extension and code reuse. Moreover, Moltres depends on the \gls{MOOSE} 
framework, \cite{gaston_physics-based_2015} another \gls{LGPL} code that itself 
leans on LibMesh \cite{kirk_libmesh:_2006}, a
\gls{LGPL} finite element library, and PetSc \cite{satish_balay_petsc_2015}, a
\gls{BSD}-licensed toolkit for solving nonlinear equations yielded by 
discretizing PDEs. \gls{MOOSE} and LibMesh translate weak PDE forms defined by
applications (e.g. Moltres) into residual and Jacobian
functions. These functions are the inputs into PetSc Newton-Raphson solution routines. All
codes use MPI for parallel communication and are easily deployed on
massively-parallel cluster-computing platforms. \gls{MOOSE} applications by
default use monolithic and implicit methods ideal for closely-coupled
and multi-scale physics, such as the model problem described
in this work. However, Moltres can also use explicit
time-stepping routines as well as segregated solution methods, making it 
extensible to myriad future modeling challenges.

@@

\FloatBarrier
\clearpage
\printglossary[type=\acronymtype]
\bibliographystyle{unsrt}
\bibliography{Moltres}
\end{document}

>>>>

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
interest in the past decade, with many new nuclear companies proposing both
fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_neutronics_2016}. Two
key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
utilization and no radiation damage constraint on attainable fuel
burn-up. Together, these attributes result in significantly reduced core fissile
inventories and spent nuclear fuel mass 
\cite{gif_generation_2008,gif_generation_2015}.  
Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
burning actinides and extending fuel resources.

\gls{MSR} modeling efforts describe steady-state and
transient behavior. Krepel et al. extended the in-house \gls{LWR}
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. That work compared DYN3D-MSR against
experimental \gls{MSRE} data and then used it to simulate local fuel channel
blockages as well as local temperature perturbations. In a similar vein, Kophazi
et. al. used iterative coupling between in-house three-dimensional neutronic and
one-dimensional heat conduction models DALTON and THERM to analyze normal 
\gls{MSRE} operation as well as channel-blocking-incident
transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
effects of heat transfer coefficients as well as thermal
coupling between fuel channels through moderator heat conduction. More recently,
Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
\gls{MSBR} using the commercial finite element package COMSOL
Multiphysics \cite{cammi_multi-physics_2011}. That work directly solved the 
fuel salt velocity field, used heterogeneous group constants
in fuel and moderator regions, and employed a software package (COMSOL)
intrinsically designed for coupled multi-physics simulation.
Additionally, Aufiero et. al \cite{aufiero_development_2014} have begun to 
approach transient simulations in the \gls{MSFR} by directly coupling Serpent 2 
Monte Carlo neutronics with OpenFOAM \cite{weller_tensorial_1998} thermal-hydraulics.

@@

Moltres is an open source code licensed under \gls{LGPL} terms so the 
\gls{MSR} community can freely use, interrogate, and improve it.  Its openness 
is a defining characteristic and promotes
quality through transparency and ease of peer review. In the era of
GitHub\cite{github_build_2017} and international scientific collaboration,
open and modern software practices must be employed in order for nuclear
engineering simulation capability to enable discovery and support the regulatory
needs presented by new reactor designs. In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to
enable extension and code reuse. Moreover, Moltres depends on the \gls{MOOSE} 
framework, \cite{gaston_physics-based_2015} another \gls{LGPL} code that itself 
leans on LibMesh \cite{kirk_libmesh:_2006}, a
\gls{LGPL} finite element library, and PetSc \cite{satish_balay_petsc_2015}, a
\gls{BSD}-licensed toolkit for solving nonlinear equations yielded by 
discretizing PDEs. \gls{MOOSE} and LibMesh translate weak PDE forms defined by
applications (e.g. Moltres) into residual and Jacobian
functions. These functions are the inputs into PetSc Newton-Raphson solution routines. All
codes use MPI for parallel communication and are easily deployed on
massively-parallel cluster-computing platforms. \gls{MOOSE} applications by
default use monolithic and implicit methods ideal for closely-coupled
and multi-scale physics, such as the model problem described
in this work. However, Moltres can also use explicit
time-stepping routines as well as segregated solution methods, making it 
extensible to myriad future modeling challenges.

@@

\FloatBarrier

\section{Acknowledgments}

All figures in this paper were generated using the python package yt
\cite{turk_yt:_2011}. The package engauge-digitizer
\cite{mark_mitchell_markummitchell/engauge-digitizer:_2017} was used to convert
rasterized \gls{MSRE} line plots into point data for plotting alongside Moltres
data.

\clearpage
\printglossary[type=\acronymtype]
\bibliographystyle{unsrt}
\bibliography{Moltres}
\end{document}
